---
title: "Topic Modelling Visualisation Example"
output: html_notebook
---

This is a visualisation example for [tidyToPān](https://doi.org/10.5281/zenodo.3605354). After we have produced a topic model in tidyToPān for the `testdata/RScripts_TopicModelling_TEDonly_final.csv` data, we can load the data into R likes this:

```{r}
library(tidyverse)
theta <- read_csv("www/models/TEDTalkCTM/20201126-1044/tab/theta.csv") %>%
  select(-X1,-text) %>%
  rename(Talk_ID = identifier)
theta
```

We also want additional metadata from the sample data set, so we import that data too:

```{r}
metadata <- read_csv("testdata/RScripts_TopicModelling_TEDonly_final.csv") %>%
  select(Talk_ID,event,duration,published,views) 
metadata
```

And then combine them:

```{r}
fusionedData <- inner_join(metadata, theta)
fusionedData
```

Now we want to make the data longer to visualise it easier accross variables in our metadata:

```{r}
longfusionedData <- fusionedData %>% pivot_longer(6:ncol(fusionedData), names_to = "Topic", values_to = "theta")
longfusionedData
```
Finally, we can start visualising the topics for instance the topic `feel_children_social_experience_happiness_lives_course` and `dollars_country_million_countries_money_africa_billion` across time:

```{r}
library(ggthemes)
library(lubridate)
selection <- c("feel_children_social_experience_happiness_lives_course","dollars_country_million_countries_money_africa_billion")
longfusionedData %>%
  filter(Topic %in% selection) %>%
  filter(theta > .1) %>%
  mutate(Date = mdy(published)) %>%
  ggplot(aes(Date, theta, fill = Topic)) +
  geom_col(position = "dodge2") +
  scale_fill_fivethirtyeight() +
  theme_wsj() +
  coord_cartesian(ylim = c(0,1))
  
```

Or all topics in April 2010:
```{r}
longfusionedData %>%
  filter(theta > .1) %>%
  mutate(Date = mdy(published)) %>%
  filter(year(Date) == 2010) %>%
  filter(month(Date) == 4) %>%
  ggplot(aes(Date, theta, fill = Topic)) +
  geom_col() +
  theme_fivethirtyeight()
```


Or which topics were most talked about
```{r}
longfusionedData %>%
  mutate(talkedAbout = map2_dbl(duration, theta, function(x,y){(period_to_seconds(hms(x)) * y) / 60})) %>%
  group_by(Topic) %>%
  summarise(`Topics talked about (weighted min)` = sum(talkedAbout, na.rm = T)) %>%
  ggplot() +
  geom_col(aes(Topic, `Topics talked about (weighted min)`, fill = Topic), show.legend = F) +
  theme_tufte() +
  scale_fill_hue() +
  coord_flip()
```
